---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# hydroscoper

The goal of hydroscoper is to provide an interface to the greek National Databank for Hydrological and Meteorological Information  at <http://kyy.hydroscope.gr/> with functions for stations, timeseries and raw data downloading.

## Installation

You can install hydroscoper from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("kvantas/hydroscoper")
```

## Stations list

This is a basic example which shows you how to get the stations list from the Hydroscope database:

```{r example}
library(hydroscoper)
stations <- get_stations()
head(stations[c("ID", "WaterDivisionID", "Name", "Owner", "Type")])
```

The abbreviations in the Owner column are:

* MEE: Ministry of Environment and Energy
* NOA: National Observatory of Athens

Other owners are Universities, Prefectures of Greece etc.
