---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# hydroscoper

The goal of **hydroscoper** is to provide an interface to the greek National Databank for Hydrological and Meteorological Information,  [Hydroscope](<http://kyy.hydroscope.gr/>), with functions for stations, timeseries and raw data downloading.

The stations and timeseries lists in Hydroscope are in greek, so this package transforms the Unicode text to Latin. Also, translates various terms in english. Finally, the **hydroscoper** provides a function to get raw timeseries data into a tidy dataframe.

## Installation

You can install **hydroscoper** from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("kvantas/hydroscoper")
```

## Stations list

This is a basic example which shows you how to get the stations list from the Hydroscope database:

```{r example}
library(hydroscoper)
stations <- get_stations()
head(stations[c("ID", "WaterDivisionID", "Name", "Owner", "Type")])
```

The abbreviations in the Owner column are:

* MEE: Ministry of Environment and Energy
* NOA: National Observatory of Athens
* Other owners are Universities, Prefectures of Greece etc.
