---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# hydroscoper

The goal of **hydroscoper** is to provide an interface to the Greek National Databank for Hydrological and Meteorological Information, [Hydroscope](<http://kyy.hydroscope.gr/>). It provides functions for downloading stations and timeseries data.

The stations and timeseries data in Hydroscope are in Greek, so this package transforms the Unicode text to Latin, and translates various Greek terms to English. Finally, the **hydroscoper** provides a function to convert raw timeseries' data into a tidy dataframe.

## Installation

You can install **hydroscoper** from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("kvantas/hydroscoper")
```

## Stations list

This is a basic example which shows you how to get the stations list from the Hydroscope database:

```{r example stations}
library(hydroscoper)
stations <- get_stations()
head(stations[c("ID", "WaterDivisionID", "Name", "Owner", "Type")])
```

The abbreviations in the Owner column are:

* MEE: Ministry of Environment and Energy
* NOA: National Observatory of Athens
* Other owners are Universities, Prefectures of Greece etc.

## Stations coordinates

With the following code you can get the coordinates and the elevation for the meteorological stations from Ministry of Environment and Energy in the Water Division of Crete, GR13:

```{r example coords}
library(plyr)
crete_stations <-subset(stations, WaterDivisionID == 'GR13' & Owner == 'MEE')
crete_coords <- ldply(crete_stations$ID, function(x) {get_coords(x)})
head(crete_coords)
```


