---
title: "Getting Hydroscope's data"
author: "Konstantinos Vantas"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

This vignette shows how to create a tidy data frame for the stations' and time series' data from Hydroscope. We will use all the Hydroscope's sub-domains.

## Download data

With the following code we can download Hydroscope's sub-domains' data to a named list. Note that it will take some time, depending on your internet connection and the Hydroscope's servers availability/traffic.

```{r}
library(hydroscoper)
library(tibble)
library(plyr)

subdomain <- c("kyy", "ypaat", "emy", "deh")

# download all databases
hydro_data <- lapply(subdomain, function(x)get_database(x))
names(hydro_data) <- subdomain

```

## Stations

We must check if there are specific variables at each sub-domain's stations' data, because we will merge these data to a new data frame.

```{r}
# check stations variables
vars <- c("id", "name", "owner", "point", "altitude", "water_basin",
          "water_division")

ldply(subdomain, function(id) {
  vars %in% names(hydro_data[[id]]$stations)
})

# check water_basin, water_division and owner variables
vars2 <- c("id", "name")
ldply(subdomain, function(id) {
  (vars2 %in% names(hydro_data[[id]]$water_basin)) &
  (vars2 %in% names(hydro_data[[id]]$water_division)) &
  (vars2 %in% names(hydro_data[[id]]$owner))
})
```

With the following code we will create a tidy data frame with the stations data. Note that the Greek terms are translated to English.
```{r}
stations <- ldply(subdomain, function(id){

  tmp <-  hydro_data[[id]]

  # extract dataframes to join
  wbas <- tmp$water_basins[c("id", "name")]
  wdiv <- tmp$water_divisions[c("id", "name")]
  owners <- tmp$owners[c("id", "name")]

  # remove area from water_basin
  wbas$name <- laply(wbas$name, function(y) gsub("\\([^()]*\\)", "", y))

  # translate names
  wdiv$name <- hydro_translate(wdiv$name, "division")
  owners$name <- hydro_translate(owners$name, "owner")

  # rename dataframes
  names(wbas) <- c("water_basin", "water_basin_name")
  names(wdiv) <- c("water_division", "water_division_name")
  names(owners) <- c("owner", "owner_name")

  # merge data
  res <- merge(tmp$stations, wbas, by = "water_basin", all.x = TRUE)
  res <- merge(res, wdiv, by = "water_division", all.x = TRUE)
  res <- merge(res, owners, by = "owner", all.x = TRUE)

  # create coords
  coords <- hydro_coords(res$point)


  data.frame(station_id = as.integer(res$id),
             name = as.character(res$name),
             water_basin = res$water_basin_name,
             water_division = res$water_division_name,
             owner = res$owner_name,
             longitude = as.numeric(coords$long),
             latitude = as.numeric(coords$lat),
             altitude = as.numeric(res$altitude),
             subdomain = rep(id, nrow(res)),
             stringsAsFactors = FALSE)

})
stations <- as_tibble(stations)
stations
```

## Time series

Similarly, we will check if there are specific variables at each sub-domain's time series' data. Note that `deh` sub-domain uses a different API and does not have the variables `start_date_utc` and `end_date_utc` in the `timeseries` table.

```{r}
vart <- c("id", "gentity", "start_date_utc", "end_date_utc", "variable",
          "time_step", "unit_of_measurement")
ldply(subdomain, function(id) {
  vart %in% names(hydro_data[[id]]$timeseries)
})

# use NA to fill missing values in deh$timeseries
vart[!(vart %in%  names(hydro_data$deh$timeseries))]
hydro_data$deh$timeseries$start_date_utc <- NA
hydro_data$deh$timeseries$end_date_utc <- NA

# check variables and timesteps
vart2 <- c("id", "descr")
ldply(subdomain, function(id) {
  (vart2 %in% names(hydro_data[[id]]$variables)) &
  (vart2 %in% names(hydro_data[[id]]$time_steps))
})

# check unit_of_measurement
vart3 <- c("id", "symbol")
ldply(subdomain, function(id) {
  vart3 %in% names(hydro_data[[id]]$units)
})
```

With the following code we will, also, create a tidy data frame with the time series data with translated terms.

```{r}
# create stations' dataframe
timeseries <- ldply(subdomain, function(id){
  
  tmp <-  hydro_data[[id]]
  
  # create data frames to join
  var_names <- tmp$variables[c("id", "descr")]
  ts_names <-  tmp$time_steps[c("id", "descr")]
  ts_units <-tmp$units[c("id", "symbol")]
  
  # translate names
  var_names$descr <- hydro_translate(var_names$descr, "variable")
  ts_names$descr <- hydro_translate(ts_names$descr, "timestep")
  
  # rename data frames
  names(var_names) <- c("variable", "variable_name")
  names(ts_names) <- c("time_step", "time_step_name")
  names(ts_units) <- c("unit_of_measurement", "unit_of_measurement_name")
  
  # merge data
  res <- merge(tmp$timeseries, var_names, by = "variable", all.x = TRUE)
  res <- merge(res, ts_names, by = "time_step", all.x = TRUE)
  res <- merge(res, ts_units, by = "unit_of_measurement", all.x = TRUE)
  
  data.frame(
    "timeser_id" = as.integer(res$id),
    "station_id" = as.integer(res$gentity),
    "variable" = as.character(res$variable_name),
    "timestep" = as.character(res$time_step_name),
    "units" = as.character(res$unit_of_measurement_name),
    "start_date" = as.character(res$start_date_utc),
    "end_date" = as.character(res$end_date_utc),
    "subdomain" = rep(id, nrow(res)), 
    stringsAsFactors = FALSE)
})
timeseries <- as.tibble(timeseries)
timeseries
```

