---
title: "An introduction to `hydroscoper`"
author: "Konstantinos Vantas"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{An introduction to hydroscoper}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## What is Hydroscope?

[Hydroscope](http://www.hydroscope.gr/) is the  Greek National Data Bank for Hydrological and Meteorological Information, a result of long-standing efforts by numerous Greek scientists in collaboration with various companies and associations. It was implemented in three phases, funded by the Ministry of Development, the Ministry of Environment and Energy and the European Union.

This National Data Bank provides several data sources from various organisations via a web interface. Each participating organisation keeps its data on its own server using a database system for the storage and management of information. These organisations are:

* Ministry of Environment and Energy.
* Ministry of Rural Development and Food.
* National Meteorological Service.
* National Observatory of Athens.
* Greek Prefectures.
* Public Power Corporation.

The above data are structured as tables and space separated text files, but are in Greek, thus limiting their usefulness. Another issue with Hydroscope is the lack of comprehensive look-up tables about the available data, which are spread across many different databases.  

## What does `hydroscoper`?

`hydroscoper` provides functionality for automatic retrieval and translation of Hydroscope's data to English.  The main functions that can be utilized is the family of functions, `get_stations`, `get_timeseries`, `get_data`, etc., to easily download Hydroscope's data as [tibbles](http://tibble.tidyverse.org/). 

The package covers Hydroscope's data sources using the Enhydris API. The Enhydris database is implemented in PostgreSQL and details about the database can be found [here](http://bit.ly/2D0cZgA),  and about the Web-service API [here](http://bit.ly/2FlRtBB).

### Internal datasets

The internal datasets of the package can be used to run queries on the available Hydroscope's stations and time series data, reducing the time needed for downloading and [data wrangling](http://bit.ly/1KslZb7), as these data are rarely modified.  These datasets are:

#### `stations`

It is a comprehensive look-up table with geographical and ownership information of the available stations in all Hydroscope's databases. The variables are: 

  1. `station_id` The station's ID.
  2. `name` The station's name.
  3. `water_basin` The station's Water Basin.
  4. `water_division` The station's Water Division.
  5. `owner` The station's owner.
  6. `longitude` The station's longitude in decimal degrees, [ETRS89](http://bit.ly/2kJwFuf).
  7. `latitude` The station's latitude in decimal degrees, [ETRS89](http://bit.ly/2kJwFuf).
  8. `altitude` The station's altitude, meters above sea level.
  9. `subdomain` The corresponding Hydroscope's database.


#### `timeseries`

It is also a look-up table with all the available measurements for a given station in a  given Hydroscope's  database, with units of measurement and times of those measurements. The variables are:

  1. `time_id` The time series ID.
  2. `station_id` The corresponding station's ID.
  3. `variable` The time series variable type.
  4. `timestep` The timestep of time series.
  5. `units` The units of the time series.
  6. `start_date` The starting date of time series values.
  7. `end_date` The ending date of time series values.
  8. `subdomain` The corresponding Hydroscope's database.


## Data sources

 * Ministry of Environment and Energy, National Observatory of Athens and Greek Prefectures, `http://kyy.hydroscope.gr/`.
 * Ministry of Rural Development and Food, `http://ypaat.hydroscope.gr`.
 * National Meteorological Service, `http://emy.hydroscope.gr`.
 * Greek Public Power Corporation, `http://deh.hydroscope.gr`.

Note that:

1. Only the two Ministries allow to download time series values freely.
2. `ypaat`, `emy` and `kyy` sub-domains are maintained  by the National Technical University Of Athens and these servers work seamlessly.
3. `deh` sub-domain is maintained  by the Greek Public Power Corporation and occasionally the server is down.

## Example

This is a basic example which shows how to get the stations' and time series' data from the Hydroscope's Ministry of Environment and Energy database, http://kyy.hydroscope.gr/.

Load libraries:

```{r load_libraries}
library(hydroscoper)
library(ggplot2)
library(tibble)

```

We will use the package's data `stations` and `timeseries`, to reduce the time needed with data munging. We can subset the station's data for the `kyy` sub-domain with:

```{r subset_data}
# load data
data("stations")

# subset stations data
kyy_stations <- subset(stations, subdomain == "kyy")

# view kyy stations
kyy_stations
```

Let's plot these stations using the package's dataset `greece_borders`.

```{r kyy_stations_map}
ggplot() + 
  geom_polygon(data = greece_borders,
               aes(long, lat, group = group),
               fill = "grey",
               color = NA) +
  geom_point(data = kyy_stations,
             aes(x = longitude, y = latitude),
             color = "#E64B35FF") +
  coord_fixed(ratio=1) +
  theme_bw()
```


To get the time series' data for the station `200200` (http://kyy.hydroscope.gr/stations/d/200200/) we can use:

```{r subset_timeseries}
station_ts <- subset(timeseries, station_id == 200200)
station_ts
```

We can download the station's  precipitation time series **56** (http://kyy.hydroscope.gr/timeseries/d/56/):

``` {r get_timeseries}
ts_raw <- get_data(subdomain = "kyy", time_id = 56)
ts_raw
```

Let's create a plot:

``` {r plot_time_series}
ggplot(data = ts_raw, aes(x = date, y = value))+
  geom_line()+
  labs(title= "30 min precipitation", 
       subtitle = "station 200200",
       x="Date", y = "Rain height (mm)")+
  theme_classic()
```



