---
title: "Using hydroscoper to get stations' and time-series' data"
author: "Konstantinos Vantas"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using hydroscoper to get stations' and time-series' data}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)
```

# Introduction

This vignette shows how to create a tidy dataframe for the stations' and time series' data from Hydroscope. The subdomain of Hydroscope that we will apply the package's functions is http:/kyy.hydroscope.gr (Ministry of Environment and Energy).

## Get database values

The following code shows how to download the data from kyy to a list.

```{r database_creation}
# load libraries
library(hydroscoper)
library(tibble)
# get data from kyy
kyy_data <- get_database("kyy")

```

# Stations data

## Coordinates

To create a data frame with the stations latitude and longitude we use the `get_coords` function:

```{r create_stations_coords}
coords <- get_coords(kyy_data$stations$point)
```

## Names translations

Next, we will create meaningful names for the stations data.

```{r}
# create names data frames
wbas_names <- merge(x = kyy_data$stations$water_basin,
                  y = kyy_data$water_basins[c("id", "name")],
                  all.x = TRUE,
                  by.x = "water_basin",
                  by.y = "id")
wd_names <- merge(x = kyy_data$stations$water_division,
                  y = kyy_data$water_divisions[c("id", "name")],
                  all.x = TRUE,
                  by.x = "water_division",
                  by.y = "id")
own_names <- merge(x = kyy_data$stations$owner,
                   y = kyy_data$owners[c("id", "name")],
                    all.x = TRUE,
                  by.x = "owner",
                  by.y = "id")

# transate names
# own_names$name <- hydro_translate(own_names$name, "owner")
# wd_names$name <- hydro_translate(wd_names$name, "division")
```

## Stations' data frame

Finally, we will create a tidy data frame with the stations values:
```{r stations_dataframe}

stations <- tibble(
  "station_id" = as.numeric(kyy_data$stations$id),
  "name" = as.character(kyy_data$stations$name),
  "water_basin" = as.character(wbas_names$name),
  "water_division" = as.character(wd_names$name),
  "owner" = as.character(own_names$name),
  "longitude" = as.numeric(coords$long),
  "latitude" = as.numeric(coords$lat),
  "altitude" = as.numeric(kyy_data$stations$altitude)
)
stations
```

# Timeseries

## Names and terms translation

We will create meaningful names for the time series' data.

```{r timeseries_names}
# create names data frames
var_names <- merge(x = kyy_data$timeseries$variable,
                  y = kyy_data$variables[c("id", "descr")],
                  all.x = TRUE,
                  by.x = "variable",
                  by.y = "id")
ts_names <-  merge(x = kyy_data$timeseries$time_step,
                  y = kyy_data$time_steps[c("id", "descr")],
                  all.x = TRUE,
                  by.x = "time_step",
                  by.y = "id")

ts_units <- merge(x = kyy_data$timeseries$unit_of_measurement,
                  y = kyy_data$units[c("id", "symbol")],
                  all.x = TRUE,
                  by.x = "unit_of_measurement",
                  by.y = "id")

# translate names
var_names$descr <- hydro_translate(var_names$descr, "variable")
ts_names$descr <- hydro_translate(ts_names$descr, "timestep")


```

```{r timeseries_dataframe}
timeseries <- tibble(
  "timeser_id" = as.numeric(kyy_data$timeseries$id),
  "station_id" = as.numeric(kyy_data$timeseries$gentity),
  "variable" = as.character(var_names$descr),
  "timestep" = as.character(ts_names$descr),
  "units" = as.character(ts_units$symbol),
  "start_date" = as.character(kyy_data$timeseries$start_date_utc),
  "end_date" = as.character(kyy_data$timeseries$end_date_utc)
)
timeseries
```

