---
title: "Hydroscope's stations with available data"
author: "Konstantinos Vantas"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

This vignette shows how to get Hydroscope's stations with available time series for downloading.
The sub-domains of Hydroscope with these data are:

* Ministry of Environment and Energy http:/kyy.hydroscope.gr
* Ministry of Rural Development and Food, http://ypaat.hydroscope.gr

## Subset data

The following code shows how to subset the data, using the package's data sets:

```{r subset_data}
library(hydroscoper)

data("stations")
data("timeseries")

# subset data
st_data <- subset(stations, subdomain == "kyy" |  subdomain =="ypaat")
time_data <- subset(timeseries, subdomain == "kyy" |  subdomain =="ypaat")
```

From Hydroscope's `r nrow(stations)` stations there are `r nrow(st_data)` from the sub-domains `kyy` and `ypaat`. Out of these stations lets examine how many have time series:

```{r stations_with_timeseries}
st_data <- st_data[st_data$station_id %in% time_data$station_id,]
```

Only `r nrow(st_data)` seems to have time series.

## Exploring data

We can create a map with the stations with data, using the ggmap package, with:

```{r create_map, message=F, warning=F}

library(ggmap)

# create map
map <- get_map(
    location = c(lon = mean(stations$longitude, na.rm = TRUE),
                 lat = mean(stations$latitude, na.rm = TRUE)),
    maptype = "toner-background",
    color = 'bw',
    zoom = 6)
p <- ggmap(map)

p +
  geom_point(data = st_data,
             aes(x = longitude, y = latitude),
             fill = 'red',
             shape = 21,
             alpha = 0.8,
             size = 2) +
  scale_fill_brewer(palette = "Set1")+
  xlim(19.5, 29) +
  ylim(34, 41.5)
```

Although there is a large number of stations, there is a heterogeneity in the coverage of the country.

These stations record a different set of variables. With the following code we can examine the number of the available time series per variable.

```{r}
head(sort(table(time_data$variable), decreasing = TRUE), n = 10)

```

The variable of precipitation is recorded with various time steps per station. There are pluviograph records mostly with a time step of 30 minutes and rain gauge 24-hour measurements.

```{r}
sort(table(time_data$timestep[time_data$variable == "precipitation"]), 
     decreasing = TRUE)
```



